---
title: "STAT5120: Homework 5" 
author: "Yunlu Li"
fontsize: 12pt
geometry: margin=1in
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, highlight=FALSE)

```

## Problem 1
### (a)
```{r}
setwd("/Users/yunluli/Desktop/stat5120/hw5")
data <- read.table("Senic.txt", header=TRUE ,sep="")
attach(data)
result<-lm(InfctRsk~Stay+Cultures+Age+Census+Beds) 
anova(result)
```
From the ANOVA table above, we have SSR($\beta_5$|$\beta_1$,$\beta_2$,$\beta_3$,$\beta_4$)=0.028.

### (b)
```{r}
```
The increment in the variability of InfctRsk that is explained by the predictors, by adding Beds to an existing set of four predictors (Stay, Cultures, Age, Census), is 0.028.

### (c)
```{r}
summary(result)
```
Age, Census, Beds appear to be not significant based on t-statistics above. 

### (d)
```{r}
reduced<-lm(InfctRsk~Stay+Cultures)
anova(reduced,result)
```
$H_0: \beta_3=\beta_4=\beta_5=0$.
$H_a:$ at least one of $\beta_3, \beta_4, \beta_5$ is non zero.
The F statistic is 1.7812 and the p-value is 0.1551, so we cannot reject the null hypothesis. This means Age, Census, Beds can be dropped from the model. 

### (e)
```{r}
summary(reduced)
```
The estimated regression equation is $\hat y= 0.805491+0.275472x_1+0.056451x_2$.

## Problem 2
### (a)
```{r}
library(faraway) 
data(seatpos)
attach(seatpos)
result<-lm(hipcenter~., data=seatpos) 
summary(result)
```
The p-value associated with F statistic is very small. However, individual t-statistic indicates that none of predicators is significant given the presence of other predicators. R^2 is 0.6866.

### (b)
The samll p-value associated with F statistic suggests that the response is significantly linearly related to
at least one of the predictors, but individual t-statistic indicates that none of predicators is significant given the presence of other predicators. This shows the sign of multicollinearity.

###(c)
```{r}
round(cor(seatpos),3)
```
Some pairs of predicators show strong pairwise correlation. 

### (d)
```{r}
vif(result)
```
HtShoes and Ht have very high VIF, indicating that there is serious multicollinearity.

### (e)
```{r}
round(cor(seatpos[,3:8]),3)
```
The six preddicators are highly correlated to each other.

### (f)
I would like to keep HtShoes, since it is most highly correlated to other predicators.

### (g)
```{r}
reduced<-lm(hipcenter~Age+Weight+HtShoes) 
vif(reduced)
```
Since the VIFs are less than 5, so multicollinearity is not a concern.

### (h)
```{r}
anova(reduced,result)
```
$H_0: \beta_4=\beta_5=\beta_6=\beta_7=\beta_8=0$.
$H_a:$ at least one of $\beta_4, \beta_5, \beta_6, \beta_7, \beta_8$ is non zero.
The F statistic is 0.5863 and the p-value is 0.7103, so we cannot reject the null hypothesis. This means Ht, Seated, Arm, Thigh, and Leg can be dropped from the model. 

### (i)
```{r}
plot(reduced$fitted.values,reduced$residuals,main="Residual Plot of Reduced Model")
abline(h=0,col="red")
acf(reduced$residuals, main="ACF of Reduced Model")
```
From the residual plot, the assumptions for the multiple regression model are satisfied. The residuals fall in a horizontal band around 0 with constant variance, and have no apparent pattern. The ACF plot indicates the residuals are uncorrelated. 

### (j)
```{r}
reduced
```
$\hat y = 532.877125 + 0.557597x_1 - 0.008688x_2 - 4.178042x_3$





